%\chapter{Obsah CD}
%\chapter{Manual}
%\chapter{Konfigrační soubor}
%\chapter{RelaxNG Schéma konfiguračního soboru}
%\chapter{Plakat}

\chapter{Parametry původního servlet kontejneru v Jenkins CI} \label{prilohaParametry}
    V této příloze jsou  uvedeny parametry, které v systému Jenkins CI poskytuje
    servlet kontejner. Uvedené parametry jsou přehledem umožňujícím čtenáři
    detailnější náhlédnutí do možností aktuálního kontejneru, ale 
    nejsou blíže rozebírány a popisovány. Pro věcnou správnost 
    jsou parametry ponechány ve formátu i formulaci jak jsou 
    sepsány v návodu použití a tedy i v původním jazyce, kterým je angličtina.

    \medskip
    Seznam možných parametrů je následující:
    \begin{itemize}
       \item{\texttt{--httpPort}               = set the http listening port. -1 to disable, Default is 8080}
       \item{\texttt{--httpListenAddress}      = set the http listening address. Default is all interfaces}
       \item{\texttt{--httpDoHostnameLookups}  = enable host name lookups on incoming http connections (true/false). Default is false}
       \item{\texttt{--httpKeepAliveTimeout}   = how long idle HTTP keep-alive connections are kept around (in ms; default 5000)?}
       \item{\texttt{--httpsPort}              = set the https listening port. -1 to disable, Default is disabled
                                  if neither --httpsCertificate nor --httpsKeyStore are specified,
                                  https is run with one-time self-signed certificate.}
       \item{\texttt{--httpsListenAddress}     = set the https listening address. Default is all interfaces}
       \item{\texttt{--httpsDoHostnameLookups} = enable host name lookups on incoming https connections (true/false). Default is false}
       \item{\texttt{--httpsKeepAliveTimeout}   = how long idle HTTPS keep-alive connections are kept around (in ms; default 5000)?}
       \item{\texttt{--httpsKeyStore}          = the location of the SSL KeyStore file.}
       \item{\texttt{--httpsKeyStorePassword}  = the password for the SSL KeyStore file. Default is null}
       \item{\texttt{--httpsCertificate}       = the location of the PEM-encoded SSL certificate file.
                                  (the one that starts with '-----BEGIN CERTIFICATE-----')
                                  must be used with --httpsPrivateKey.}
       \item{\texttt{--httpsPrivateKey}       = the location of the PEM-encoded SSL private key.
                                  (the one that starts with '-----BEGIN RSA PRIVATE KEY-----')}
       \item{\texttt{--httpsKeyManagerType}    = the SSL KeyManagerFactory type (eg SunX509, IbmX509). Default is SunX509}
       \item{\texttt{--spdy}               = Enable SPDY. See http://wiki.eclipse.org/Jetty/Feature/NPN}
       \item{\texttt{--ajp13Port}              = set the ajp13 listening port. -1 to disable, Default is disabled}
       \item{\texttt{--ajp13ListenAddress}     = set the ajp13 listening address. Default is all interfaces}
       \item{\texttt{--controlPort}            = set the shutdown/control port. -1 to disable, Default disabled}
       
       \item{\texttt{--handlerCountStartup}    = set the no of worker threads to spawn at startup. Default is 5}
       \item{\texttt{--handlerCountMax}        = set the max no of worker threads to allow. Default is 40}
       \item{\texttt{--handlerCountMaxIdle}    = set the max no of idle worker threads to allow. Default is 5}
       
       \item{\texttt{--sessionTimeout}         = set the http session timeout value in minutes. Default to what webapp specifies, and then to 60 minutes}
       \item{\texttt{--mimeTypes=ARG}          = define additional MIME type mappings. ARG would be \\EXT=MIMETYPE:EXT=MIMETYPE:...
                                  (e.g., xls=application/vnd.ms-excel:\\wmf=application/x-msmetafile)}
       \item{\texttt{--maxParamCount=N}        = set the max number of parameters allowed in a form submission to protect
                                  against hash DoS attack (oCERT \#2011-003). Default is 10000.}
       \item{\texttt{--usage / --help}         = show this message}
       \item{\texttt{--version}                = show the version and quit}
       
       \item{\texttt{--realmClassName}               = Set the realm class to use for user authentication. Defaults to ArgumentsRealm class}
       
       \item{\texttt{--argumentsRealm.passwd.<user>} = Password for user <user>. Only valid for the ArgumentsRealm realm class}
       \item{\texttt{--argumentsRealm.roles.<user>}  = Roles for user <user> (comma separated). Only valid for the ArgumentsRealm realm class}
       
       \item{\texttt{--fileRealm.configFile}         = File containing users/passwds/roles. Only valid for the FileRealm realm class}
       
       \item{\texttt{--accessLoggerClassName}        = Set the access logger class to use for user authentication. Defaults to disabled}
       \item{\texttt{--simpleAccessLogger.format}    = The log format to use. Supports \\combined/common/resin/custom (SimpleAccessLogger only)}
       \item{\texttt{--simpleAccessLogger.file}      = The location pattern for the log file(SimpleAccessLogger only)}
    \end{itemize}


